% IEEE standard conference template; to be used with:
%   spconf.sty  - LaTeX style file, and
%   IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------

\documentclass[letterpaper]{article}
\usepackage{spconf,amsmath,amssymb,graphicx}
\usepackage{array}
\usepackage{nicematrix}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{caption}

% Example definitions.
% --------------------
% nice symbols for real and complex numbers
\newcommand{\R}[0]{\mathbb{R}}
\newcommand{\C}[0]{\mathbb{C}}

% bold paragraph titles
\newcommand{\mypar}[1]{{\bf #1.}}

% Title.
% ------
\title{Parallelizing the Smith-Waterman algorithm for genome sequencing}
%
% Single address.
% ---------------
\name{Kosta Stojiljkovic, Han Yao Choong, Langwen Huang, Benjamin Langer} 
\address{Progress report - Design of Parallel and High-Performance Computing - Group 15}

% For example:
% ------------
%\address{School\\
%		 Department\\
%		 Address}
%
% Two addresses (uncomment and modify for two-address case).
% ----------------------------------------------------------
%\twoauthors
%  {A. Author-one, B. Author-two\sthanks{Thanks to XYZ agency for funding.}}
%		 {School A-B\\
%		 Department A-B\\
%		 Address A-B}
%  {C. Author-three, D. Author-four\sthanks{The fourth author performed the work
%		 while at ...}}
%		 {School C-D\\
%		 Department C-D\\
%		 Address C-D}
%

\begin{document}
%\ninept
%
\maketitle
%

\section{Introduction}

Genome sequencing has become a promising field tool that is hypothesized to facilitate researchers to find the root cause (and subsequently the cure) for a number of genetic diseases in the future. \cite{Maekinen.2015}

% Diviation from proposal
The investigation into three different algorithms in the initial proposal (see attached below) was discarded in favor of a more thorough and deeper look into one of them (namely Smith-Waterman). From a computer science perspective all of these algorithms are rather similar, consequently the team decided to focus its efforts on the one which is most relevant in the given domain.

\section{Parallelization strategy}
In our first attempts two different strategies were pursued that either exploit the inherent structure of the problem or the overall nature of the problem.

\mypar{Fine-grained approach} A major step of Smith-Waterman algorithm is the calculation of a similarity matrix which measure how closely parts of the tow sequences resemble each other. Each entry in the matrix depends only on its neighbors to the west, north, and north-west. For example, calculating the value encircled in red in Figure 1 only depends on the black encircled entries. Exploiting these data dependencies, each anti-diagonal in the similarity matrix may be calculated independently from each other. 

\setlength{\extrarowheight}{1.5mm}
\begin{figure}[!h]
	\centering
	$\begin{pNiceMatrix}%
		[name=mymatrix,
		first-col,
		first-row,
		columns-width = 0.3cm
		]
		&   & \mathbf{T} & \mathbf{G} & \mathbf{T} & \mathbf{T} \\
		& 0 & 0 & 0 & 0 & 0 \\
		\mathbf{G} & 0 & 0 & 3 & 1 & 0 \\
		\mathbf{G} & 0 & 0 & 3 & 1 & 0 \\
		\mathbf{T} & 0 & 3 & 1 & 6 & 4 \\
		\mathbf{T} & 0 & 3 & 1 & 4 & 9 \\
		
	\end{pNiceMatrix}$
	\begin{tikzpicture}[remember picture,overlay]
		\draw[line width=0.25mm, red](mymatrix-4-4)circle (2mm);
		\draw[line width=0.25mm](mymatrix-3-4)circle (2mm);
		\draw[line width=0.25mm](mymatrix-4-3)circle (2mm);
		\draw[line width=0.25mm](mymatrix-3-3)circle (2mm);
	\end{tikzpicture}
	\caption{Data dependencies between entries}
\end{figure}%

\mypar{Coarse-grained approach} 



\section{Work split}



\begin{center}
	\begin{tabular}{ | m{1.5cm} | m{6cm} | } 
		\hline
		Name & Main focus* \\ 
		\hline
		Kosta & Coarse-grain approach, MPI \\ 
		Langwen & CMake setup, Matrix transformation \\ 
		Han & Bioinf input, OpenMP \\
		Benjamin & Testing, base algorithm implementation \\
		\hline
	\end{tabular}
\end{center}
*Various teammates also contributed actively and significantly to other fields.



% References should be produced using the bibtex program from suitable
% BiBTeX files (here: bibl_conf). The IEEEbib.bst bibliography
% style file from IEEE produces unsorted bibliography list.
% -------------------------------------------------------------------------
\bibliographystyle{IEEEbib}
\bibliography{bibl_conf}

\end{document}

